
% \cvevent{Uintah High School}{}{}{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{\href{https://github.com/jrmoulton/leviosa}{Reverse Enginnering Standing Desk}}
\begin{itemize}
	\item Reverse engineered the communication between the user controller and the motor controller.
		A voltmeter to find the power lines, logic analyzer to watch signals on all 6 ethernet wires.
		Recognized as a half-duplex uart communication. Fully decoded the structure of frames, packets and
		segments.
	\item Built an embedded application to act as a remote control using bluetooth on dual-core esp32s3. (in progress)
\end{itemize}
\smallskip
\cvproject{\href{https://github.com/jrmoulton/interpreter-rs}{Compiler from Scratch}}
\begin{itemize}
    \item Side Project: An interpreter and a compiler with a custom parser for a programmign language with a
		rust like syntax. Compiles to a bytecode and is run in a custom virtual machine with high quality
		error handling and messages to the end user.
	\item Class: CS5300 C compiler from scratch in Java
\end{itemize}
\smallskip
\cvproject{\href{https://docs.rs/dacx0501/latest/dacx0501/index.html}{DACx0501 Library}}
\begin{itemize}
    \item A Rust library supporting the Texas Instruments x0501 family of DACs using the
        rust embedded-hal traits
\end{itemize}
\smallskip
\cvproject{Open Source Contributions}
\begin{itemize}
    \item \textbf{esp-hal}: Work on embedded-hal SPI implementation
    \item \textbf{slint-ui}: Treesitter parser and various additions
    \item \textbf{floem}: Various efforts to improve the UI framework
\end{itemize}
\smallskip
\cvproject{\href{https://github.com/jrmoulton/Aggietime}{Aggietime Clock API}}
\begin{itemize}
	\item A web app that acts as a man in the middle to
		re-expose the USU Aggietime API in an accessible way. This app parses
		tokens from the HTML responses of Aggietime and then forwards along a
		proper request with the credentials from the end user.
\end{itemize}
\smallskip
\cvproject{Dense Neural Network from Scratch}
\begin{itemize}
	\item A dense, fully connected neural network made to recognize hanwritten
		digits from the MNIST dataset written from scratch in numpy.
\end{itemize}
\smallskip
\cvproject{\href{https://github.com/jrmoulton/jrmoulton-web}{Static Website Generator}}
\begin{itemize}
	\item Personal website and blog with content being written in markdown and then generated using a
		custom static site generator with awesome code syntax highlighting and theming.
\end{itemize}
\smallskip
\cvproject{\href{https://github.com/jrmoulton/Mandelbrot-Multithreaded}{Multithreaded Mandelbrot Generator}}
\begin{itemize}
	\item A Mandelbrot image generator that splits the 
		image's rows to be processed by multiple threads. The final output format 
		is a bpm where the image header information is written as a stream of raw 
		bytes followed by the image data.
\end{itemize}
\smallskip

% \medskip
% \raggedleft\textbf{Github Profile} \\
% \smallskip
% \raggedleft\qrcode{https://github.com/jrmoulton}
